Extending the Advanced Forensic Format to accommodate Multiple Data Sources, Logical Evidence, Arbitrary Information and Forensic Workflow

### 2009-05-19 paper/paper.tex
bls-paper Ignore-this: da8191ba56f9ce08571c88872042044a

\begin{abstract}
Forensic analysis requires the acquisition and management of many
different types of evidence, including individual disk drives, RAID
sets, network packets, memory images, and extracted files. Often the
same evidence is reviewed by several different tools or examiners in
different locations. We propose a backwards-compatible redesign of the
Advanced Forensic Format---an open, extensible file format for storing
and sharing of evidence, arbitrary case related information and
analysis results among different tools. The new specification, termed
AFF4, was designed to be simple to implement, bult upon the well
supported ZIP file format specification. AFF4 implementation have
downward compatability with existing AFF files.
\end{abstract}

\section{Introduction}
Storing and managing digital evidence is becoming increasingly more
difficult, as the volume and size of digital evidence increases. The
type of what consitutes evidence has also evolved to include data
other than disk images, such as memory images, network images and
regular files. Preserving digital evidence is an important part of
most digital investigations\cite{carrier:event-based}, and managing
the evidence in a distributed organization is now emerging as a
critical requirement.

@@

\subsection{Prior Work}
In recent years there has been a steady and growing interest in the
actual file formats and containers used to store digital
evidence. Early practitioners created exact bit-for-bit copies
(commonly referred to as ``dd images''). More recently, proprietary
software systems for making and authenticating ``images'' of digital
evidence are commonly used
(e.g. \cite{safeback,ilook,encase}). PyFlag\cite{pyflag} introduced a
``seekable gzip'' format that allowed disk images to be stored in a
form that was compressed but allowed random-access to evidence data
necessary for forensic analysis.

The Expert Witness Forensic (EWF) file format was originally developed
for Encase\cite{encase}, but then adopted by other vendors
\cite{libewf}. The EWF file format also compresses the image into 32kb
chunks which are stored back to back in groupings inside the file. The
format contains multiple tables containing relative indexes to these
compressed chunks which are also stored within the volume. EWF volumes
have a maximum size of 2Gb and therefore usually split an image across
many volumes. EWF provides for a small number of predefined metadata
fields to be stored within the file format.

@@

Both the AFF and EWF file formats are designed to store a single
image, and any metadata implicitely refers to that image. Therefore,
these formats in themselves have a limited metadata model which is
unable to exist outside the context of the image itself.  But AFF went
beyond merely specifying metadata as an addition to the forensic
evidence itself. Metadata forms an essential part of the file format,
with the same metadata system storing both essential information
required to read the image itself, as well as non-essential
metadata. AFF allows the use of arbitrary name/value pairs to store
metadata, but it also stored critical information such as sector size
and device serial number using the same metadata representation
system. \verb+Aimage+, the AFF hard disk acquisition tool, not only
stores the image, but additionally stores a description of the tool
itself, the version of AFFLIB used to create the image, the computer
on which the image was made, the operator of the tool, the user
supplied parameters supplied to the tool.

@@

\item \emph{A Relation or Fact} is a statement about an AFF Object which
  expresses some property of the object. The relation comprises of a
  tuple of (Subject, Attribute, Value). All metadata is reduced to
  this tuple notation.

@@

The AFF4 model treats metadata as an abstract concept which may exist
independently from the data itself. We term {\em metadata} to be a set
of statements about objects, written in tuple notations (Subject,
Attribute, Value), where {\em Subject} is the URN of the object the
statement is made about. An \emph{Attribute} can be any kind of value, such
as the sector size of a device, a device capacity, or the name of the
person who performed an imaging operation. A \emph{Value} is the value
of the attribute. Using this system we are able to store
arbitrary attributes about any object in the AFF4
universe. Additionally, as these statements are universally scoped,
they may be stored anywhere.

@@

It is important to emphesise that Volumes are merely containers which
provide storage for segments. There is no restriction of which
segments can be stored by any particular volume. For example, the
segments which make up a single Image stream may be stored in a number
of volumes (splitting the image in some way among them). Similarly,
the segments representing a number of streams may be stored in the
same volume.

@@

\section{Identity Object}
AFF4 defines a \emph{Statement} as a collection of facts, or
(subject, attribute, value) tuples. Listing \ref{statement}
illustrates a collection of facts encoded in the standard AFF4
notation (SHA254 hashes are base64 encoded).

@@

To verify the signatures, the AFF4 library loads the stored
certificate, then checks the signature for each statement. If a
statement is verified (i.e. deemed as correct according to the
identity), the facts within it are checked. Note that it is possible
for multiple identities to sign the same data.

>>>>

\begin{abstract}
Forensic analysis requires the acquisition and management of many
different types of evidence, including individual disk drives, RAID
sets, network packets, memory images, and extracted files. Often the
same evidence is reviewed by several different tools or examiners in
different locations. We propose a backwards-compatible redesign of the
Advanced Forensic Format---an open, extensible file format for storing
and sharing of evidence, arbitrary case related information and
analysis results among different tools. The new specification, termed
AFF4, is designed to be simple to implement, bult upon the well
supported ZIP file format specification. Furthermore, the AFF4 implementation has
downward compatability with existing AFF files.
\end{abstract}

\section{Introduction}
Storing and managing digital evidence is becoming increasingly more
difficult, as the volume and size of digital evidence increases. Evidence
sources have also evolved to include data
other than disk images, such as memory images, network images and
regular files. Preserving such digital evidence is an important part of
most digital investigations\cite{carrier:event-based}, and managing
the evidence in a distributed organization is now emerging as a
critical requirement.

@@

\subsection{Prior Work}
In recent years there has been a steady and growing interest in the
actual file formats and containers used to store digital
evidence. Early practitioners created exact bit-for-bit copies
(commonly referred to as ``dd images''). More recently, proprietary
software systems for making and authenticating ``images'' of digital
evidence have become common
(e.g. \cite{safeback,ilook,encase}). PyFlag\cite{pyflag} introduced a
``seekable gzip'' format that allowed disk images to be stored in a
form that was compressed but allowed random-access to evidence data
necessary for forensic analysis.

The Expert Witness Forensic (EWF) file format was originally developed
for Encase\cite{encase}, but then adopted by other vendors
\cite{libewf}. The EWF file format similarly compresses the image into 32kb
chunks which are stored back to back in groupings inside the file. The
format employs tables of relative indexes to the
compressed chunks to improve random access efficienct. EWF volumes
have a maximum size limit of 2Gb and therefore usually split an image across
many files. EWF provides for a small number of predefined metadata
fields to be stored within the file format.

@@

Both the AFF and EWF file formats are designed to store a single
image, and any metadata implicitely refers to that image. Therefore,
these formats in themselves have a limited metadata model which is
unable to exist outside the context of the image itself.  But the AFF went
beyond merely specifying metadata as an addition to the forensic
evidence itself. Metadata forms an essential part of the file format,
with the same metadata system storing both essential information
required to read the image itself, as well as non-essential
metadata. AFF allows the use of arbitrary name/value pairs to store
metadata, but it also stored critical information such as sector size
and device serial number using the same metadata representation
system. \verb+Aimage+, the AFF hard disk acquisition tool, not only
stores the image, but additionally stores a description of the tool
itself, the version of AFFLIB used to create the image, the computer
on which the image was made, the operator of the tool, the user
supplied parameters supplied to the tool.

@@

\item \emph{A Relation} is a factual statement which is used either to describe
  a relationship between two AFF Objects, or to describe some property of an object. The relation comprises of a
  tuple of (Subject, Attribute, Value). All metadata is reduced to
  this tuple notation.

@@

The AFF4 model treats metadata as an abstract concept which may exist
independently from the data itself. We term {\em metadata} to be a set
of statements about objects, written in tuple notations (Subject,
Attribute, Value), where {\em Subject} is the URN of the object the
statement is made about. An \emph{Attribute} can be any kind of value or relationship, such
as the sector size of a device, a device capacity, or the name of the
person who performed an imaging operation. A \emph{Value} is the value
of the attribute, which is either another URN, or some textual value. Using this system we are able to store
arbitrary attributes about any object in the AFF4
universe. Additionally, as these statements are universally scoped,
they may be stored anywhere.

@@

It is important to emphasise that Volumes are merely containers which
provide storage for segments. There is no restriction of which
segments can be stored by any particular volume. For example, the
segments which make up a single Image stream may be stored in a number
of volumes (splitting the image in some way among them). Similarly,
the segments representing a number of streams may be stored in the
same volume.

@@

\section{Identity Object}
AFF4 defines a \emph{Statement} as a collection of relations, or
(subject, attribute, value) tuples. Listing \ref{statement}
illustrates a collection of relations encoded in the standard AFF4
notation (SHA254 hashes are base64 encoded).

@@

To verify the signatures, the AFF4 library loads the stored
certificate, then checks the signature for each statement. If a
statement is verified (i.e. deemed as correct according to the
identity), the relations within it are checked. Note that it is possible
for multiple identities to sign the same data.
